Hypertension and microbiome

### 2019-01-02 rrbiome.Rmd
Maaslin

# Genus

@@

```{r prepare maaslin, eval = FALSE}

pheno <- t(meta(sample_data(pseq_filtered)))
sample.ids <- colnames(pheno)
phfg.pseq.rel <- microbiome::transform(pseq_filtered, "compositional")
abud.rel <- abundances(phfg.pseq.rel)

rownames(abud.rel) <- sapply(rownames(abud.rel),
                             function (genus) gsub("(.*) \\(+(.+)\\)", '\\1.\\2', genus))

merged <- rbind(sample.ids, pheno, abud.rel)
write.table(t(merged), file="merged_phfinrisk_genus.tsv", sep='\t', 
            quote=FALSE, row.names=FALSE, col.names=TRUE)

variables <- rownames(pheno)
variables_wo_ctrls <- variables[!variables %in% c("BL_AGE","BMI","SEX")]
data <- file("maaslin_config.config" , open='wt')
pcl.contents <- c("Matrix: Metadata",
                  paste(c("Read_PCL_Rows: BL_AGE,BMI,SEX",variables_wo_ctrls), collapse=","),
                  "",
                  "Matrix: Adundance",
                  "Read_PCL_Rows: Archaea.Archaea-")
writeLines(pcl.contents, con=data)
close(data)
```

```{r run maaslin, eval = FALSE} 
Maaslin("merged_phfinrisk_genus.tsv",
        "maaslin",
        strInputConfig = "maaslin_config.config",
        strModelSelection="none",
        dSignificanceLevel = 1.0, 
        fAllvAll = TRUE,
        strForcedPredictors = c("BL_AGE", "BMI", "SEX"))

>>>>

# Connection between genus and blood pressure

@@

```{r prepare maaslin}

prepare.maaslin <- function (pseq,
                             tsvfile = "merged_phfinrisk_genus.tsv",
                             conffile = "maaslin_config.config",
                             includedvars = c("BL_AGE", "BMI", "SEX")) {
    pheno <- t(microbiome::meta(phyloseq::sample_data(pseq)))
    sample.ids <- colnames(pheno)
    phfg.pseq.rel <- microbiome::transform(pseq, "compositional")
    abud.rel <- abundances(phfg.pseq.rel)
    rownames(abud.rel) <- sapply(rownames(abud.rel), function (genus) gsub("(.*) \\(+(.+)\\)", '\\1.\\2', genus))
    merged <- rbind(sample.ids, pheno, abud.rel)
    write.table(t(merged), file = tsvfile, sep='\t', quote=FALSE, row.names=FALSE, col.names=TRUE)
    data <- file(conffile , open='wt')
    pcl.contents <- c("Matrix: Metadata",
                      paste(c("Read_PCL_Rows: ", paste(includedvars, collapse=",")), collapse = ""),
                      "",
                      "Matrix: Adundance",
                      "Read_PCL_Rows: Archaea.Archaea-")
    writeLines(pcl.contents, con=data)
    close(data)
}

```{r run maaslin} 
maaslin.force.vars <- c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03", "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09")
prepare.maaslin(pseq.genus,
                 tsvfile = "merged_phfinrisk_genus.tsv",
                conffile = "maaslin_config.config",
                includedvars = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION", maaslin.force.vars))

Maaslin("merged_phfinrisk_genus.tsv",
        "maaslin",
        strInputConfig = "maaslin_config.config",
        strModelSelection="none",
        dSignificanceLevel = 1.0, 
        fAllvAll = TRUE,
        strForcedPredictors = maaslin.force.vars)
